%-------------------------
% Resume in Latex
% Author: Alexander Gilbert (content) / Claude (template)
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-2pt}\scshape\bfseries\normalsize
}{}{0em}{}[\color{black}\vspace{-10pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Alexander Gilbert} \\ \vspace{3pt}
    \small
    \faMobile* \hspace{.5pt} \href{tel:8153537804}{(815) 353-7804} ~
    \faAt \hspace{.5pt} \href{mailto:alexander.paul.gilbert@gmail.com}{alexander.paul.gilbert@gmail.com} ~
    % \faGlobe \hspace{.5pt} \href{http://www.alexpgilbert.com}{www.alexpgilbert.com} ~
    \faMedium \hspace{.5pt} \href{https://medium.com/@alexander.paul.gilbert}{@alexander.paul.gilbert} \\
    \faGithub \hspace{.5pt} \href{https://github.com/Alex-Gilbert}{@Alex-Gilbert} \\
    \faMapMarker* \hspace{.5pt} Sleepy Hollow, IL (Greater Chicago Area)
\end{center}

%----------PROFESSIONAL SUMMARY----------
\section{Professional Summary}
\small{
Principal Graphics Engineer with 9+ years of experience architecting and shipping GPU-accelerated solutions. Terminal enthusiast who leverages Neovim and CLI-centric workflows to design robust CI/CD pipelines with Docker, Kubernetes, and GitHub Actions, ensuring on-time delivery across multiple teams and projects. Proven leader of cross-disciplinary teams, author of GPU-optimization white papers, and driver of scalable, production-ready solutions in complex simulation and rendering systems.
}

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in]
  \item \textbf{Languages:} C++, Rust, Python, C\#, WGSL, GLSL, HLSL
  \item \textbf{APIs \& Frameworks:} WGPU, Vulkan, OpenGL, DirectX, GNM (PlayStation)
  \item \textbf{Tools:} Neovim, Git, CMake, Docker, Kubernetes, GitHub Actions, Jira, RenderDoc
  \item \textbf{Optimization:} Performance profiling, memory hierarchy tuning, shader optimization
  \item \textbf{Workflows:} CI/CD pipeline design, automated testing, code review best practices
  \item \textbf{3D Math:} Linear algebra, quaternions, projections, transformations
\end{itemize}

%----------AREAS OF EXPERTISE----------
\section{Areas of Expertise}
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Software Engineering:} Rapid adoption of new technologies with strategic implementation; expertise in object-oriented and data-oriented programming paradigms; efficient architecture for complex systems
    \item \textbf{Real-time rendering pipelines:} ray tracing, rasterization, PBR, post-processing, VFX
    \item \textbf{GPU architecture \& optimization:} memory hierarchies, workload distribution, performance tuning
    \item \textbf{Cross-platform engine design:} desktop, mobile, web, VR/AR deployment
    \item \textbf{Automated build \& deployment:} containerized CI/CD, automated validation for graphics pipelines
    \item \textbf{Geospatial visualization systems:} MVT rendering, tile caching, quadkey indexing, map projections, large-scale data rendering
\end{itemize}

%----------EXPERIENCE----------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Defcon AI}{2023 - Present}
{Principal Engineer}{Remote}
\resumeItemListStart
\resumeItem{Led the Advanced Engineering Group (AEG), a four-person \textbf{multidisciplinary} team to establish unified technical standards for frictionless innovation.}
\resumeItem{Architected and maintained Skyshark, an interactive, high-performance, portable geographic data visualization engine using \textbf{Rust} and \textbf{wgpu} for real-time rendering of complex geospatial datasets.}
\resumeItem{Rapidly established robust build pipelines and \textbf{CI/CD} workflows using \textbf{Docker}, \textbf{Kubernetes}, and \textbf{GitHub Actions}, ensuring on-time delivery of internal projects across multiple Impact Level (IL) environments.}
\resumeItem{Improved cross-team collaboration leading to the successful delivery of ARTIV, a logistics planning and optimization tool developed under Air Force contract.}
\resumeItem{Authored a white paper on a Newton–Raphson–enhanced gradient-descent \textbf{GPU-accelerated} algorithm to minimize aircraft behavior calculations in a global simulation, achieving real-time processing of 100,000+ aircraft and accurately estimating uninterrupted simulation runtime.}
\resumeItem{\textbf{Shipped Products:} Artiv, Skyshark}
\resumeItemListEnd

\resumeSubheading
{Independent Graphics Engineering Consultant}{2022 - 2023}
{Self-Employed}{Remote}
\resumeItemListStart
\resumeItem{\textbf{Defcon AI:} Architected a high-performance visualization engine using \textbf{Unity3D}; developed custom \textbf{rasterization} solutions; created cross-platform geospatial rendering engine with \textbf{GPU-acceleration}.}
\resumeItem{\textbf{Dassault Systemes:} Integrated proprietary \textbf{raytracer} into SOLIDWORKS Visualize; debugged rendering issues and optimized \textbf{GPU-performance}; contributed to the successful release of SOLIDWORKS Visualize 2023.}
\resumeItemListEnd

\resumeSubheading
{Here Technologies}{2021 – 2022}
{Senior Software Engineer}{Remote}
\resumeItemListStart
\resumeItem{Developed and optimized \textbf{procedural-generation} algorithms for Cesium 3D Tiles, enabling scalable geospatial visualization.}
\resumeItem{Engineered data-conversion pipelines to transform proprietary geodata formats into optimized 3D representations.}
\resumeItem{Built automated validation systems for 3D output, reducing QA cycle time by several days per release.}
\resumeItem{\textbf{Product Delivered:} 3D Premier Cities}
\resumeItemListEnd

\resumeSubheading
{LevelEx}{2020 - 2021}
{Graphics Engineer}{Chicago, IL}
\resumeItemListStart
\resumeItem{Implemented advanced \textbf{real-time rendering} techniques including \textbf{subsurface scattering}, \textbf{soft body simulation}, \textbf{X-ray visualization}, and \textbf{ultrasound} effects for medical training applications.}
\resumeItem{Developed custom tooling that enabled artists to model and animate complex vascular structures with realistic blood flow and tissue interactions.}
\resumeItem{Created specialized \textbf{shader effects} and extended \textbf{Unity3D's} rendering pipeline for medically accurate tissue rendering.}
\resumeItem{Optimized high-performance graphics solutions for mobile and \textbf{VR/AR} platforms, ensuring 60+ FPS on target devices.}
\resumeItem{\textbf{Shipped Products:} CardioEx, Amgen Repatha Racer, Philips Vascular, Magic Leap BrainLab Sales Demo}
\resumeItemListEnd

\resumeSubheading
{Sony PlayStation}{2018 - 2020}
{Graphics Engineer}{San Mateo, CA}
\resumeItemListStart
\resumeItem{Provided graphics engineering support to PlayStation developers through DevNet.}
\resumeItem{Created developer tools and authored documentation on \textbf{PlayStation graphics architecture}.}
\resumeItem{Developed HDR Scopes, a critical tool for PlayStation 4 \& 5 developers.}
\resumeItem{Enhanced the PlayStation SDK with custom graphics tools.}
\resumeItem{Presented technical sessions on emerging \textbf{GPU technologies} and rendering techniques.}
\resumeItem{\textbf{Shipped Products:} HDR Scopes for PlayStation 4 \& 5}
\resumeItemListEnd

\resumeSubheading
{Incredible Technologies}{2016 - 2018}
{Platform / Graphics Engineer}{Vernon Hills, IL}
\resumeItemListStart
\resumeItem{Developed a custom high-performance font rendering solution that enabled dynamic text at high resolution while maintaining 60+ FPS, including custom integration with \textbf{3ds Max} for artists.}
\resumeItem{Rearchitected the legacy VM-based build system into a distributed pipeline leveraging developer workstations—virtually eliminating build queues and cutting average build wait times from hours to under 15 minutes, dramatically boosting engineering productivity.}
\resumeItem{Created specialized \textbf{shader effects} and graphics tools, directly supporting multiple in-house game studios.}
\resumeItem{Eliminated critical rendering bottlenecks and implemented efficient \textbf{GPU-based} visual effects, significantly improving performance on resource-constrained casino hardware.}
\resumeItem{\textbf{Shipped Products:} Infinity V55, Infinity Pilot, Infinity Super Skybox, Crazy Money Gold, Super Sky Wheel, Dreamstar}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------CERTIFICATIONS & PUBLICATIONS----------
\section{Courses \& Publications}
\resumeSubHeadingListStart
\resumeSubItem{\textbf{White Paper}: GPU-Accelerated Minimum Variable Time Step Solution, Defcon AI Internal Publication, 2023}
\resumeSubItem{\textbf{Published Course}: Swords and Shovels: Combat System for Unity, Pluralsight, 2019}
\resumeSubHeadingListEnd

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart
\resumeEducationHeading
{University of Illinois at Chicago}{2015}
{Bachelor of Science in Mathematics}{Chicago, IL}
\resumeSubHeadingListEnd


\end{document}
